Training a Gaming Agent on Brainwaves

### 2019-12-04 ErrP.tex
Actualizo algunos nombres de archivos

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The field of Brain Computer Interfaces (BCI) has seen a bloom in the past few years. One of its applications is the training of systems using signals originated from the human brain. Out of all the methods used to acquire information from the central nervous system, the one that has gained most popularity is Electroencephalography (EEG), mainly because of its effectiveness, low cost and its noninvasive characteristic.
Event-related potential (ERP) are brain signals that are time-locked to a particular event. Error-related potential (ErrP) are a particular type of ERP that  can be elicited by a person who attends a recognizable error. When subjects observe an agent who makes a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
Reinforcement Learning (RL) is an Artificial Intelligence approach where an agent tries to maximize rewards obtained while interacting with an unknown environment.  In this work, a gaming agent is trained using RL, and the feedback obtained from human critic observers.  Results show that there is an effective transfer of information and that the agent learns successfully to solve the game efficiently.
\end{abstract}

@@

After the form is filled out, a short description of the procedure is given to each subject. They are only told that the objective of the agent is to reach the goal and the four movements that the agent can make. When this concludes, the subject is introduced to the wireless digital EEG device (g.Nautilus, g.Tec, Austria) that they have to wear during the brainwave session. It has eight electrodes (g.LADYbird, g.Tec, Austria) on the positions Fz, Cz, Pz, Oz, P3, P4, PO7 and PO8, identified according to the 10-20 International System, with a reference set to the right ear lobe and ground set as the AFz position. The electrode contact points are adjusted applying conductive gel until the impedance values displayed by the program g.NeedAccess (g.Tec, Austria) are within the desired range. This process takes between 10 and 15 minutes. After this step, the subject is instructed to close their eyes and the same program is used to check the live channel values so that there are no dead ones and the expected values are displayed for eye movements or muscle chewing.

Once the headset is correctly applied, the OpenVibe Acquisition Server program, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured with a sampling rate of $250$ Hz. A $50$ Hz notch filter is applied to filter out power line noise. An additional bandpass filter between $0.5$ Hz and $60$ Hz is applied as well. Data is handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel for the stimulus, which corresponds to a game movement performed by the agent.  After everything is connected, the subject seats in a comfortable chair in front of a computer screen. The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject can not distinguish the components of the game that appear on the screen.  The dataset is published on the IEEE DataPort initiative~\cite{6emh-wb46-19}.

@@

In the case for subject 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively. Figures \ref{fig:avg_steps} E and \ref{fig:avg_steps} F show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.  These results are also consistent with their ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both subjects, where the area under the curve are close to chance level.  Both subjects have less recorded data from the sessions in comparison to the rest of the subjects.   This variation in performance for different subjects has been studied extensively in BCI.  Besides low data samples there could be other reasons that may be affecting the classification accuracy:  it may be due to cognitive reasons, this being the subject not paying extensively attention to the game dynamics, very low Signal-To-Noise Ratio (SNR) of the ErrP component or even the BCI-illiteracy phenomena where the specific subject's signals do not contain the expected component response~\cite{Yousefi2019}.

\begin{figure}[h!]
\captionsetup[subfigure]{justification=centering}
\begin{subfigure}{0.25\textwidth}
    \centering
    \includegraphics[scale=0.2]{Images/Classification_test/roc_manuel.png}
\end{subfigure}
\begin{subfigure}{0.25\textwidth}
    \centering
    \includegraphics[scale=0.2]{Images/Classification_test/roc_marta.png}  
\end{subfigure}
\caption{ROC Curves for subjects 5 (up) and 6 (down)}
\label{fig:rocsubjects}
\end{figure}

%These results are consistent with fig. \ref{fig:roc:manuel} and fig. \ref{fig:roc:marta}, which show that the signal classification for these subjects hasn't been particularly successful.

@@

%\begin{figure*}[ht!]
%    \centering
%    \begin{subfigure}[t]{0.5\textwidth}
%        \centering
%        \includegraphics[height=1.2in]{Images/Average_steps/marta_santiago.png}
%        \caption{Lorem ipsum}
%    \end{subfigure}%
%    ~ 
%    \begin{subfigure}[t]{0.5\textwidth}
%        \centering
%        \includegraphics[height=1.2in]{Images/Average_steps/alex_jose.png}
%        \caption{Lorem ipsum, lorem ipsum,Lorem ipsum, lorem ipsum,Lorem ipsum}
%    \end{subfigure}
%    \caption{Caption place holder}
%\end{figure*}

@@

This work aims to to state whether ErrP signals could be used to train a gaming agent using reinforcement learning. The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.

@@

While classifying, the better performing classifier is Logistic Regression. One important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.  It is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal. On the other hand, the percentage of false negatives is generally higher.  However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.

\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
\centering
\includegraphics[scale=0.12]{Images/Classification_test/matrix_alex.png}
\includegraphics[scale=0.12]{Images/Classification_test/matrix_jose.png}\\
\includegraphics[scale=0.12]{Images/Classification_test/matrix_juan.png}
\includegraphics[scale=0.12]{Images/Classification_test/matrix_santiago.png}
\end{subfigure}
\caption{Confusion Matrix for subjects 1,3,4 and 8. Darker colors show higher values.  It can be seen the lower percentage of false positives (upper right corner of each chart).}
\label{fig:confusionmatrix}
\end{figure}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The field of Brain Computer Interfaces (BCI) has seen a bloom in the past few years. One of its applications is the training of systems using signals originated from the human brain. Out of all the methods used to acquire information from the central nervous system, the one that has gained most popularity is Electroencephalography (EEG), mainly because of its effectiveness, low cost and its noninvasive characteristic.
Event-related potential (ERP) are brain signals found on EEG that are time-locked to a particular event. Error-related potential (ErrP) are a particular type of ERP that  can be elicited by a person who attends a recognizable error. When subjects observe an agent who makes a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
Reinforcement Learning (RL) is an Artificial Intelligence approach where an agent tries to maximize rewards obtained while interacting with an unknown environment.  In this work, a gaming agent is trained using RL, and the feedback obtained from brainwaves of human critic observers.  Results show that there is an effective transfer of information and that the agent learns successfully to solve the game efficiently.
\end{abstract}

@@

After the form is filled out, a short description of the procedure is given to each subject. They are only told that the objective of the agent is to reach the goal and the four movements that the agent can make. When this concludes, the subject is introduced to the wireless digital EEG device (g.Nautilus, g.Tec, Austria) that they have to wear during the brainwave session. It has eight electrodes (g.LADYbird, g.Tec, Austria) on the positions Fz, Cz, Pz, Oz, P3, P4, PO7 and PO8, identified according to the 10-20 International System, with a reference set to the right ear lobe and ground set as the AFz position. The electrode contact points are adjusted applying conductive gel until the impedance values displayed by the program g.NeedAccess (g.Tec, Austria) are within the desired range. This process takes between 10 to 15 minutes. After this step, the subject is instructed to close their eyes and the same program is used to check the live channel values so that there are no dead ones and the expected values are displayed for eye movements or muscle chewing.

Once the headset is correctly applied, the OpenVibe Acquisition Server program, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured with a sampling rate of $250$~Hz. A $50$~Hz notch filter is applied to filter out power line noise. An additional bandpass filter between $0.5$~Hz and $60$~Hz is applied as well. Data is handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel for the stimulus, which corresponds to a game movement performed by the agent.  After everything is connected, the subject seats in a comfortable chair in front of a computer screen. The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject can not distinguish the components of the game that appear on the screen.  This dataset has been published on the IEEE DataPort initiative~\cite{6emh-wb46-19}.

@@

In the case for subject 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively. Figures \ref{fig:avg_steps} E and \ref{fig:avg_steps} F show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.  These results are also consistent with their ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both subjects, where the area under the curve are close to chance level.  Both subjects have less recorded data from the sessions in comparison to the rest of the subjects.   This variation in performance for different subjects has been studied extensively in BCI.  Besides low data samples there are other reasons affecting the classification accuracy:  cognitive reasons, this being the subject not paying extensively attention to the game dynamics, very low Signal-To-Noise Ratio (SNR) of the ErrP component or even the BCI-illiteracy phenomena where the specific subject's signals do not contain the expected component response~\cite{Yousefi2019}.

\begin{figure}[h!]
\captionsetup[subfigure]{justification=centering}
\begin{subfigure}{0.25\textwidth}
    \centering
    \includegraphics[scale=0.2]{Images/Classification_test/roc_e.png}
\end{subfigure}
\begin{subfigure}{0.25\textwidth}
    \centering
    \includegraphics[scale=0.2]{Images/Classification_test/roc_f.png}  
\end{subfigure}
\caption{ROC Curves for subjects 5 (up) and 6 (down)}
\label{fig:rocsubjects}
\end{figure}

%These results are consistent with fig. \ref{fig:roc:e} and fig. \ref{fig:roc:f}, which show that the signal classification for these subjects hasn't been particularly successful.

@@

@@

This work aims to state whether ErrP signals could be used to train a gaming agent using reinforcement learning. The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.

@@

While classifying, the better performing classifier is Logistic Regression. One important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.  It is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal. On the other hand, the percentage of false negatives is generally higher.  However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.

%However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.

\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
\centering
\includegraphics[scale=0.12]{Images/Classification_test/matrix_a.png}
\includegraphics[scale=0.12]{Images/Classification_test/matrix_c.png}\\
\includegraphics[scale=0.12]{Images/Classification_test/matrix_d.png}
\includegraphics[scale=0.12]{Images/Classification_test/matrix_h.png}
\end{subfigure}
\caption{Confusion Matrix for subjects 1,3,4 and 8. Darker colors show higher values.  It can be seen the lower percentage of false positives (upper right corner of each chart).}
\label{fig:confusionmatrix}
\end{figure}
